### 2025-07-18 getting-started.qmd
20250718 - create a function

## Installing Packages {#sec-installingPackages}

@@

@@

A function often takes particular input(s) and produces some form of output.
The name of the function is followed by parentheses; the inputs go in between the parentheses.
You can learn about a particular function and its arguments by entering a question mark before the name of the function:

@@

>>>>

## Install Packages {#sec-installingPackages}

@@

You can also install multiple packages with one line of code (replacing each package with its respective name):

install.packages(c("PACKAGE1","PACKAGE2","PACKAGE3"))
```

@@

A function often takes particular input(s) and produces some form of output.
The name of the function is followed by parentheses; the inputs go in between the parentheses.
The possible inputs that a function can accept are called "arguments".
You can learn about a particular function and its arguments by entering a question mark before the name of the function:

@@

## Create a Function {#sec-createFunction}

Functions are useful if you want to perform an operation multiple times.
Use of a function can save you time without needed to retype out all of the code each time.
For instance, let's say you want to convert temperature between Fahrenheit and Celsius, you could create a function to do that.

```{r}
convert_temperature <- function(temperature, unit = "F"){
  if(unit == "F"){ # if the input temperature(s) in Fahrenheit
    newtemp <- (temperature - 32) / (9/5)
  } else if(unit == "C"){ # if the input temperature(s) in Celsius
    newtemp <- (temperature * (9/5)) + 32
  }

  return(newtemp)
}
```

Now we can use the function to convert temperatures between Fahrenheit and Celsius.
A temperature of 32°F is equal to 0°C.
A temperature of 0°C is equal to 89.6°F.

```{r}
convert_temperature(
  temperature = 32,
  unit = "F"
)

convert_temperature(
  temperature = 32,
  unit = "C"
)
```

We can also convert the temperature for a vector of values at once:

```{r}
convert_temperature(
  temperature = c(0, 10, 20, 30, 40, 50),
  unit = "F"
)

convert_temperature(
  temperature = c(0, 10, 20, 30, 40, 50),
  unit = "C"
)
```

Because the default unit is "F", we do not need to specify the unit if our input temperatures are in Fahrenheit:

```{r}
convert_temperature(
  c(0, 10, 20, 30, 40, 50)
)
```
